---
title: "Assignment"
date: "`r Sys.Date()`"
output: 
  prettydoc::html_pretty:
    theme: "tactile"
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(dplyr)
library(readr)
library(stringr)
```

```{r, include=FALSE}
# Opening the comprehensive tidy dataset (Funda_dataset_cleaned.csv)
funda <- read.csv("/Users/anastasijaaleksova/Library/Mobile Documents/com~apple~CloudDocs/Desktop/Utrecht University/Y2P3/Introduction to R/AssignmentIntroToR/Funda_dataset_cleaned.csv") 

# Setting the date of the sale
funda$Verkoopdatum <- as.Date(funda$Verkoopdatum, format="%Y-%m-%d")

funda <- funda %>%
  arrange(Verkoopdatum) %>% # Arranges the data frame in ascending order based on the values purchase date column
  filter(Energielabel != "None") # Filters the rows in the dataframe to keep only those where the value is not equal to none

# Setting the earliest purchase date as significant value
min_funda <- min(funda$Verkoopdatum, na.rm = TRUE)

# Opening the dataset (ECB Data.csv)
interest_rates <- read.csv("/Users/anastasijaaleksova/Library/Mobile Documents/com~apple~CloudDocs/Desktop/Utrecht University/Y2P3/Introduction to R/AssignmentIntroToR/ECB Data Portal_20240318183415.csv") 

# Setting the date of the interest rate changes
interest_rates$DATE <- as.Date(interest_rates$DATE, format="%Y-%m-%d")

# Isolating the columns needed
funda <- select(funda, Verkoopdatum, Energielabel)

# Joining the two datasets together through the dates
data <- full_join(funda, interest_rates, by = c("Verkoopdatum" = "DATE"))

# Filtering the data set based on the values in the purchase date to keep only the dates greater than or equal to the minimum funda date
data <- filter(data, Verkoopdatum >= min_funda) %>%
  arrange(Verkoopdatum) %>% # Arranges the data in ascending order based on the dats
  select(-TIME.PERIOD) # Select all but TIME.PERIOD

# Create a new variable called "energy_category"
data$Energielabel <- ifelse(str_detect(data$Energielabel, "^A"), 
                            "≥A", 
                            data$Energielabel)

# Translating from Dutch to English
names(data)[1] <-  "date" 
names(data)[2] <- "energy_label" 
names(data)[3] <- "main_refinancing_rate"

names(interest_rates)[1] <-  "date" 
names(interest_rates)[3] <- "main_refinancing_rate"

interest_rates <- interest_rates %>%
  filter(date >= min_funda) %>%
  select(-TIME.PERIOD)

# Loop through each row in 'data'
for(i in 1:nrow(data)) {
  # Find the indexes of the 'interest_rates' observations where 'date' is less than or equal to 'date' in 'data'
  j <- which(interest_rates$date <= data$date[i])
  
  # Check if 'j' is not empty and the last index in 'j' is not the last observation in 'interest_rates'
  if(length(j) > 0 && max(j) < nrow(interest_rates)) {
    # Ensure 'j' refers to the last index where 'date' in 'interest_rates' <= 'date' in 'data'
    j <- max(j)
    
    # Check if 'data$date[i]' is also less than the next 'date' in 'interest_rates'
    if(data$date[i] <= interest_rates$date[j + 1]) {
      # Update 'main_refinancing_rate' in 'data' with the value from 'interest_rates' at 'j'
      data$main_refinancing_rate[i] <- interest_rates$main_refinancing_rate[j]
    }
  } 
  else {
    # Handle cases where 'data$date[i]' is before all dates in 'interest_rates' or 'j' is empty
    data$main_refinancing_rate[i] <- 0.00  # Or use the interest rate before the interest rate hike
  }
}

write.csv(data, "/Users/anastasijaaleksova/Library/Mobile Documents/com~apple~CloudDocs/Desktop/Utrecht University/Y2P3/Introduction to R/AssignmentIntroToR/data.csv", row.names = FALSE)

write.csv(interest_rates, "/Users/anastasijaaleksova/Library/Mobile Documents/com~apple~CloudDocs/Desktop/Utrecht University/Y2P3/Introduction to R/AssignmentIntroToR/interest_rates.csv", row.names = FALSE)
```

## Introduction
```{r}


```

## Data

[Funda.nl](https://www.kaggle.com/datasets/yoerireumkens/funda-sold-houses-data-raw-dutch-columns) is a popular Dutch website dedicated to real estate listings and property-related information. It serves as a comprehensive platform for individuals looking to buy, sell, or rent properties in the Netherlands. Funda.nl provides users with an extensive database of listings, including houses, apartments, and commercial properties, along with relevant details such as property specifications, photos, and pricing information. The platform also offers tools for filtering and searching for properties based on various criteria, making it a valuable resource for those interested in the Dutch real estate market. Please note that all columns in the dataset are in Dutch, a list of translations for each column is provided.

The European central Bank (ECB) HCIP dataset reflects the main refinancing interest rate which is direct monetary policy tool that plays an instrumental role in the Eurozone economic activity, i.e. economic activity in the Netherlands. Interest rates set by the ECB affect borrowing behaviour, consumer spending,  and investment, which in turn is proven to influence the real estate market. Alone, lower interest rates make borrowing cheaper, consequently boosting demand for real estate, while higher rates could dampen this demand.

The rationale behind merging these two datasets stems from the intention to explore how ECB interest rate changes correlate with trends in the real estate market in the Netherlands. This analysis can reveal insights into how macroeconomic policy impacts real estate values and sales activities over time.

The cleaning and merging process consists of several steps to ensure compatibility and relevance of the data for analysis: (explain the cleaning and merging of the two datasets)

```{r}

```

## Analysis
```{r}
```

## Conclusion
```{r}
```

